SPEI drought SN

### 2017-11-07 analysis/drought/explore_drought_spei_regional.Rmd
update regional drought

d1970 <- ggplot(spei_mean_melt1970, aes(x=date, y=value, fill=sign)) +  
  geom_bar(stat = "identity") + 
  facet_wrap(~variable, ncol=1, labeller = as_labeller(label_variables)) + 
  scale_fill_manual(values = c("pos" = "darkblue", "neg" = "red")) +
  theme_bw()  + 
  labs(title= 'Drought evolution for Sierra Nevada (From year 1995)',
    x= '',
    y='SPEI') +
  theme(strip.background = element_rect(fill = "white"),
        legend.position = "none") +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y")

>>>>

d1970 <- ggplot(spei_mean_melt1970, aes(x=date, y=value, fill=sign)) +  
  geom_bar(stat = "identity") + 
  facet_wrap(~variable, ncol=1, labeller = as_labeller(label_variables)) + 
  scale_fill_manual(values = c("pos" = "darkblue", "neg" = "red")) +
  theme_bw()  + 
  labs(title= 'Drought evolution for Sierra Nevada (From year 1970)',
    x= '',
    y='SPEI') +
  theme(strip.background = element_rect(fill = "white"),
        legend.position = "none") +
  scale_x_date(date_breaks = "2 year", date_labels = "%Y")
